### 2021-06-01 cued/additional.tex
Proof-read night before

For reference, we provide the likelihood and priors for the microcanonical SBM proposed by \citet{Peixoto-Bayesian-Microcanonical}. We have that the graph $A$ is drawn from the SBM,
%
\begin{equation}
	A \sim \textrm{DC-SBM}_{\textrm{MC}}(b, e, k),
\end{equation}
%
with edges placed uniformly at random but respecting the constraints imposed by $b, e$ and $k$. The computation of the likelihood, $p(A|k, e, b)$, is simply a case of counting the number of configurations that yield the same adjacency matrix and dividing by the total number of configurations possible. This is what gives this formulation the `microcanonical' moniker. If we consider the half-edges to be distinguishable for a moment, the total number of configurations that satisfy the $e$ constraint is,
%
\begin{equation}
	\Omega(e) = \frac{\prod_{r} e_r !}{\prod_{r,s : r < s} e_{rs}! \prod_{r} e_{rr}!!},
\end{equation}
%
where $e_r \coloneqq \sum_{s} e_{rs}$ and $(2m)!! \coloneqq 2^m m!$. Nevertheless, a great number of these $\Omega(e)$ total configurations yield the same graph $A$. We denote the number of configurations that yield the adjacency matrix $A$ with,
%
\begin{equation}
	\Xi(A) \coloneqq \frac{\prod_i k_i !}{\prod_{i,j : i < j} A_{ij} ! \prod_i A_{ii} !! }.
\end{equation}
%
Note the similarity between the forms of $\Omega(e)$ and $\Xi(A)$ as $e$ is effectively the adjacency matrix of the block-graph. With these defined we can write the overall likelihood as the ratio of the two:
%
\begin{equation}
	p(A|k,e,b) = \frac{\Xi(A)}{\Omega(e)}.
\end{equation}
%
Obviously, this form is only defined if $A$ respects the constraints imposed by $(k,e,b)$ else the likelihood is 0.

@@

Nevertheless, $\bar{U}$ decreases with $s$ indicating shorter burn-in times for larger step-sizes. However, this effect plateaus for $s>0.2$ for this particular dataset. Therefore, we choose $s=0.2$ as our step-size multiplier for the primary school dataset as this yields the best trade-off between $r_\alpha$ and $\bar{U}$. The step-sizes for the other datasets were chosen following the same argument but we do not repeat the process here.

@@

For the purposes of the FFBM model, the number of blocks $B$ is a constant 
which must be specified. If the choice of $B$ is influenced 
by the observed data, then the analysis is no longer ``fully Bayesian''
and belongs to the class of methods referred to as ``empirical Bayes.''
However, as the number of blocks only specifies the coarseness of the 
analysis, it is reasonable to allow it to vary. Indeed, 
\citet{peixoto-determine-B} shows that for a fixed 
average degree the maximum number of detectable blocks scales 
as $O(\sqrt{N})$ where $N$ is the number of vertices.

@@

Many vertex feature often take only one of several discrete values within a set. For example, with the primary school dataset \cite{schools}, a pupil's school-class can take one of 10 values from \{``1A", ``1B", ``2A", ``2B" \dots ``5A", "5B"\}.

@@

Nevertheless, this dimensionality expansion means that we should not include a bias term in our softmax as then the MAP solution is less peaked and our $\theta$-samples will have higher variance. To illustrate this point we need only look at the form of the softmax activation function with bias vector $\beta$, operating on a vector $x$ which only has one non-zero entry $x_d=1$. Component $j$ of the output is given by:
%
\begin{equation}
	\phi_j(x) = \frac{\exp(w_j^T x + \beta_j)}{\sum_{k \in [B]} \exp(w_k^T x + \beta_k)} = 
	\frac{\exp(w_{jd} + \beta_j)}{\sum_{k \in [B]} \exp({w_{kd} + \beta_k})}.
	\label{eqn:softmax-bias}
\end{equation}
%
The term $w_{kd} + \beta_k$ is effectively the new weight for component $k$ as these two terms will always appear together. The bias term $\beta_k$ is therefore an unnecessary extra degree of freedom. To illustrate this point, we set $\beta_k=\beta_0$ for all $j$. If this is the case then equation \ref{eqn:softmax-bias} can be simplified to:
%
\begin{equation}
	\phi_j(x) = \frac{\exp(\beta_0) \cdot \exp(w_{jd})}{\sum_{k \in [B]} \exp(\beta_0) \cdot \exp(w_{kd})}
	= \frac{\exp(w_{jd})}{\sum_{k \in [B]} \exp(w_{kd})}.
\end{equation}
%
This expression is independent of $\beta_0$ and so it is free to vary. This is not the whole picture as we also have the prior which introduces a regularisation term, favouring weights closer to 0. This ensures the MAP solution is unique. Nevertheless, for mutually exclusive binary feature flags, the bias term does not add to the expressiveness of the model and only serves to complicate analysis. We therefore choose to remove the bias term from the softmax.

@@

We are given samples $\{\theta^{(t)}\}_{t \in \Tcal_\theta} \sim p(\theta | A, X)$ and wish to determine the statistical significance of the weights. We adopt matrix notation for simplicity by representing $\theta$ with the $B \times D$ matrix of feature weights $W$. The question is to determine the significance of a particular feature $d$ from the sampled values of $W_{id}$ for all the values $i \in [B]$. We know that the posterior is proportional to the prior multiplied by the likelihood,
%
\begin{equation}
	p(\theta|A, X) \propto p(\theta) \cdot p(A | \theta, X),
\end{equation}
%
assuming that the feature matrix $X$ is already given. The prior term can be evaluated but the likelihood is intractable. The closest we can get is through a Monte-Carlo integration over $b$,
%
\begin{align}
	p(A | \theta, X) &= \sum_{b \in [B]^N} p(A, b | \theta, X) \nonumber \\
	&= \sum_{b \in [B]^N} p(A | b, \theta, X) \cdot p(b | \theta, X) \nonumber \\
	&= \sum_{b \in [B]^N} p(A | b) \cdot p(b | \theta, X) \nonumber \\
	&\approx \sum_{i} p\left( A | b^{(i)} \right) \quad \textrm{with} \quad b^{(i)} \sim p(b| \theta, X).
	\label{eqn:mc-likelihood}
\end{align}
%
This could be implemented for a single value of $\theta$ but such a form cannot be used to characterise the overall form of the posterior. Nevertheless, the form in~(\ref{eqn:mc-likelihood}) highlights something interesting. The likelihood is peaked around areas of $\theta$ that generate a partition $b$ that is highly likely in the SBM sense -- high $p(A|b)$. This provides the motivation for using the Laplace approximation for the posterior $p(\theta | A, X) \approx p(\theta; \hat{\mu}, \hat{\Sigma})$. Indeed, the Laplace approximation is often used for modelling the posterior in logistic classification \cite{laplace}. Marginalising over the other elements, the posterior for each element of the weight matrix $W$ can be approximated by,
%
\begin{equation}
	p(W_{ij}|A, X) \approx \Gaussian(W_{ij}|\hat{\mu}_{ij}, \hat{\sigma}_{ij}^2).
\end{equation}
%
We use the set of samples for $W$ drawn according to the exact posterior, to calculate unbiased estimates for the mean and standard deviation:
%
\begin{equation}
	\hat{\mu}_{ij} \coloneqq \frac{1}{|\Tcal_\theta|} \sum_{t \in \Tcal_\theta} W_{ij}^{(t)} \qquad \textrm{and} \qquad
	\hat{\sigma}_{ij}^2 \coloneqq \frac{1}{|\Tcal_\theta|} \sum_{t \in \Tcal_\theta} \left( W_{ij}^{(t)} - \hat{\mu}_{ij} \right)^2.
\end{equation}
%
This approximation is not exact but we can show it is accurate empirically. Indeed, if we run the primary school experiment with hyper-parameters given in Appendix \ref{appdx:hyperparams}, we can then plot histograms of the collected $W^{(t)}$-samples (for $t \in \Tcal_\theta$) and compare these to the Laplace approximation. The results are given on Figure \ref{fig:school-histogram}, which show the Laplace approximation is remarkably reliable.

@@

Using the approximation, we wish to construct a test to determine whether a particular weight value has $|W_{ij}| > c$ with high probability, where $c>0$. More specifically, we wish to decide between:
%
\begin{equation}
	\begin{aligned}
		H_0&: |W_{ij}| \leq c \\
		H_1&: |W_{ij}| > c
	\end{aligned}
\end{equation}
%
We can consider the probabilities $p(W_{ij} > c)$ and $p(W_{ij} < c)$ separately. Starting with $p(W_{ij} > c)$, we write this as,
%
\begin{align*}
	p(W_{ij} > c) &= p\left(Z > \frac{c - \hat{\mu}_{ij}}{\hat{\sigma}_{ij}}\right) \\
	&= p\left(-Z < \frac{\hat{\mu}_{ij} - c}{\hat{\sigma}_{ij}}\right)\\
	&= \Phi\left(\frac{\hat{\mu}_{ij} - c}{\hat{\sigma}_{ij}}\right),
\end{align*}
%
where $Z \sim \Gaussian(0,1)$ and $\Phi(\cdot)$ is the standard Gaussian cumulative density function. We introduce the variable $k$ to control the degree of significance of the result. Enforcing $k$ to be less than the argument of $\Phi$ gives us that: 
%
\begin{equation*}
	\hat{\mu}_{ij} - k \hat{\sigma}_{ij} > c.
\end{equation*}
%
As $\Phi(\cdot)$ is monotonically increasing, this yields the following:
%
\begin{equation}
	p(W_{ij} > c) > \Phi(k) \iff \hat{\mu}_{ij} - k \hat{\sigma}_{ij} > c.
	\label{eqn:hyp-test-positive}
\end{equation}
%
A similar argument can be made to show that:
%
\begin{equation}
	p(W_{ij} < -c) > \Phi(k) \iff \hat{\mu}_{ij} + k \hat{\sigma}_{ij} < -c.
	\label{eqn:hyp-test-negative}
\end{equation}
%
Clearly equations \ref{eqn:hyp-test-positive} and \ref{eqn:hyp-test-negative} cannot both hold simultaneously as $c, \hat{\sigma}_{ij}, k>0$. Nevertheless, a necessary and sufficient condition for one of them to hold is:
%
\begin{equation}
	(\hat{\mu}_{ij} - k \hat{\sigma}_{ij}, \hat{\mu}_{ij} + k \hat{\sigma}_{ij}) \cap (-c, +c) = \emptyset
	\label{eqn:hyp-test-empty}
\end{equation}
%
This is equivalent to saying that $\hat{\mu}_{ij}$ is at least $k$ standard deviations away from the range $(-c, c)$. We choose to reject the null hypothesis $H_0$ if and only if equation \ref{eqn:hyp-test-empty} holds. We can say with probability greater than or equal to $\Phi(k)$ that either $W_{ij} < -c$ or $W_{ij} > c$ thus rejecting the null $H_0: |W_{ij}| \leq c$.

Note that we choose to accept $H_0$ even in the case that the combined probabilities of $p(W_{ij} < -c) + p(W_{ij} > c) > \Phi(k)$, if equation \ref{eqn:hyp-test-empty} is not satisfied. This is because we wish to apply this for dimensionality reduction purposes. We only want to keep weights for which we have a confident prediction outside the range $(-c, c)$ not those that succeed by summing the two extremes of their distribution. Note that this case is very rare empirically but it nonetheless must be specified.

>>>>

For reference, we provide the likelihood for the microcanonical SBM proposed by \citet{Peixoto-Bayesian-Microcanonical}. We have that the graph $A$ is drawn from the SBM,
%
\begin{equation}
	A \sim \textrm{DC-SBM}_{\textrm{MC}}(b, e, k),
\end{equation}
%
with edges placed uniformly at random but respecting the constraints imposed by $b, e$ and $k$. The computation of the likelihood, $p(A|k, e, b)$, is simply a case of counting the number of configurations that yield the same adjacency matrix and dividing by the total number of configurations possible. This is what gives this formulation the `microcanonical' moniker. If we consider the half-edges to be distinguishable for a moment, the total number of configurations that satisfy the $e$ constraint is,
%
\begin{equation}
	\Omega(e) = \frac{\prod_{r} e_r !}{\prod_{r,s : r < s} e_{rs}! \prod_{r} e_{rr}!!},
\end{equation}
%
where $e_r \coloneqq \sum_{s} e_{rs}$ and $(2m)!! \coloneqq 2^m m!$. Nevertheless, a great number of these $\Omega(e)$ total configurations yield the same graph $A$. We denote the number of configurations that yield the adjacency matrix $A$ with,
%
\begin{equation}
	\Xi(A) \coloneqq \frac{\prod_i k_i !}{\prod_{i,j : i < j} A_{ij} ! \prod_i A_{ii} !! }.
\end{equation}
%
Note the similarity between the forms of $\Omega(e)$ and $\Xi(A)$ as $e$ is effectively the adjacency matrix of the block-graph. With these defined we can write the overall likelihood as the ratio of the two:
%
\begin{equation}
	p(A|k,e,b) = \frac{\Xi(A)}{\Omega(e)}.
\end{equation}
%
Obviously, this form is only applicable if $A$ respects the constraints imposed by $(k,e,b)$ else the likelihood is 0.

@@

Nevertheless, $\bar{U}$ decreases with $s$, indicating shorter burn-in times for larger step-sizes. However, this effect plateaus for $s>0.2$ for this particular dataset. Therefore, we choose $s=0.2$ as our step-size multiplier for the primary school dataset as this yields the best trade-off between $r_\alpha$ and $\bar{U}$. The step-sizes for the other datasets were chosen following the same argument but we do not repeat the process here.

@@

For the purposes of the FFBM model, the number of blocks $B$ is a constant 
which must be specified. If the choice of $B$ is influenced 
by the observed data, then the analysis is no longer ``fully Bayesian''
and belongs to the class of methods referred to as ``empirical Bayes''.
However, as the number of blocks only specifies the coarseness of the 
analysis, it is reasonable to allow it to vary. Indeed, 
\citet{peixoto-determine-B} shows that for a fixed 
average degree the maximum number of detectable blocks scales 
as $O(\sqrt{N})$ where $N$ is the number of vertices.

@@

Many vertex features often take only one of several discrete values within a set. For example, with the primary school dataset \cite{schools}, a pupil's school-class can take one of 10 values from \{``1A", ``1B", ``2A", ``2B" \dots ``5A", "5B"\}.

@@

Nevertheless, this dimensionality expansion means that we should not include a bias term in our softmax as then the MAP solution is less peaked and our $\theta$-samples will have higher variance. To illustrate this point, we need only look at the form of the softmax activation function with bias vector $\beta$, operating on a vector $x$ which only has one non-zero entry $x_d=1$. Component $j$ of the output is given by:
%
\begin{equation}
	\phi_j(x) = \frac{\exp(w_j^T x + \beta_j)}{\sum_{k \in [B]} \exp(w_k^T x + \beta_k)} = 
	\frac{\exp(w_{jd} + \beta_j)}{\sum_{k \in [B]} \exp({w_{kd} + \beta_k})}.
	\label{eqn:softmax-bias}
\end{equation}
%
The term $w_{kd} + \beta_k$ is effectively the new weight for component $k$ as these two terms will always appear together. The bias term $\beta_k$ is therefore an unnecessary extra degree of freedom. To illustrate this point, we set $\beta_k=\beta_0$ for all $j$. If this is the case,~(\ref{eqn:softmax-bias}) can be simplified to:
%
\begin{equation}
	\phi_j(x) = \frac{\exp(\beta_0) \cdot \exp(w_{jd})}{\sum_{k \in [B]} \exp(\beta_0) \cdot \exp(w_{kd})}
	= \frac{\exp(w_{jd})}{\sum_{k \in [B]} \exp(w_{kd})}.
\end{equation}
%
This expression is independent of $\beta_0$ and so it is free to vary. This is not the whole picture as we also have the prior which introduces a regularisation term, favouring weights closer to 0. This ensures the MAP solution is unique. Nevertheless, for mutually exclusive binary feature flags, the bias term does not add to the expressiveness of the model and only serves to complicate analysis. We therefore choose to remove the bias term from the softmax.

@@

We are given samples $\{\theta^{(t)}\}_{t \in \Tcal_\theta} \sim p(\theta | A, X)$ and wish to determine the statistical significance of the weights. We adopt matrix notation for simplicity, representing $\theta$ with the $B \times D$ matrix of feature weights $W$. The question is to determine the significance of a particular feature $d$ from the sampled values of $W_{id}$ for $i \in [B]$. We know that the posterior is proportional to the prior multiplied by the likelihood,
%
\begin{equation}
	p(\theta|A, X) \propto p(\theta) \cdot p(A | \theta, X),
\end{equation}
%
assuming that the feature matrix $X$ is already given. The prior term can be evaluated but the likelihood is intractable. The closest we can get is through a Monte-Carlo integration over $b$,
%
\begin{align}
	p(A | \theta, X) &= \sum_{b \in [B]^N} p(A, b | \theta, X) \nonumber \\
	&= \sum_{b \in [B]^N} p(A | b, \theta, X) \cdot p(b | \theta, X) \nonumber \\
	&= \sum_{b \in [B]^N} p(A | b) \cdot p(b | \theta, X) \nonumber \\
	&\approx \sum_{i} p\left( A | b^{(i)} \right) \quad \textrm{with} \quad b^{(i)} \sim p(b| \theta, X).
	\label{eqn:mc-likelihood}
\end{align}
%
This could be implemented for a single value of $\theta$ but such a form cannot be used to characterise the overall form of the posterior. Nevertheless, the form in~(\ref{eqn:mc-likelihood}) highlights something interesting. The likelihood is peaked around areas of $\theta$ that generate a partition $b$ that is highly likely in the SBM sense -- high $p(A|b)$. This provides the motivation for using the Laplace approximation for the posterior $p(\theta | A, X) \approx p(\theta; \hat{\mu}, \hat{\Sigma})$. Indeed, the Laplace approximation is often used for modelling the posterior in logistic classification \cite{laplace}. Marginalising over the other elements, the posterior for each element of the weight matrix $W$ can be approximated by,
%
\begin{equation}
	p(W_{ij}|A, X) \approx \Gaussian(W_{ij}|\hat{\mu}_{ij}, \hat{\sigma}_{ij}^2).
\end{equation}
%
We use the set of samples for $W$ drawn according to the exact posterior, to calculate unbiased estimates for the mean and standard deviation:
%
\begin{equation}
	\hat{\mu}_{ij} \coloneqq \frac{1}{|\Tcal_\theta|} \sum_{t \in \Tcal_\theta} W_{ij}^{(t)} \qquad \textrm{and} \qquad
	\hat{\sigma}_{ij}^2 \coloneqq \frac{1}{|\Tcal_\theta|} \sum_{t \in \Tcal_\theta} \left( W_{ij}^{(t)} - \hat{\mu}_{ij} \right)^2.
\end{equation}
%
This approximation is not exact but we can show it is accurate empirically. Indeed, if we run the primary school experiment with hyper-parameters given in Appendix \ref{appdx:hyperparams}, we can then plot histograms of the collected $W^{(t)}$-samples (for $t \in \Tcal_\theta$) and compare these to the Laplace approximation. The results are given on Figure \ref{fig:school-histogram}, which show the Laplace approximation is remarkably reliable.

@@

Using the approximation, we wish to construct a test to determine whether a particular weight value has $|W_{ij}| > c$ with high probability, where $c>0$. More specifically, we wish to decide between:
%
\begin{equation}
	\begin{aligned}
		H_0&: |W_{ij}| \leq c \\
		H_1&: |W_{ij}| > c
	\end{aligned}
\end{equation}
%
We can consider the probabilities $p(W_{ij} > c)$ and $p(W_{ij} < c)$ separately. Starting with $p(W_{ij} > c)$, we write this as,
%
\begin{align*}
	p(W_{ij} > c) &= p\left(Z > \frac{c - \hat{\mu}_{ij}}{\hat{\sigma}_{ij}}\right) \\
	&= p\left(-Z < \frac{\hat{\mu}_{ij} - c}{\hat{\sigma}_{ij}}\right)\\
	&= \Phi\left(\frac{\hat{\mu}_{ij} - c}{\hat{\sigma}_{ij}}\right),
\end{align*}
%
where $Z \sim \Gaussian(0,1)$ and $\Phi(\cdot)$ is the standard Gaussian cumulative density function. We introduce the variable $k$ to control the degree of significance of the result. Enforcing $k$ to be less than the argument of $\Phi$ gives us that: 
%
\begin{equation*}
	\hat{\mu}_{ij} - k \hat{\sigma}_{ij} > c.
\end{equation*}
%
As $\Phi(\cdot)$ is monotonically increasing, this yields the following:
%
\begin{equation}
	p(W_{ij} > c) > \Phi(k) \iff \hat{\mu}_{ij} - k \hat{\sigma}_{ij} > c.
	\label{eqn:hyp-test-positive}
\end{equation}
%
A similar argument can be made to show that:
%
\begin{equation}
	p(W_{ij} < -c) > \Phi(k) \iff \hat{\mu}_{ij} + k \hat{\sigma}_{ij} < -c.
	\label{eqn:hyp-test-negative}
\end{equation}
%
Clearly equations \ref{eqn:hyp-test-positive} and \ref{eqn:hyp-test-negative} cannot both hold simultaneously as $c, \hat{\sigma}_{ij}, k>0$. Nevertheless, a necessary and sufficient condition for one of them to hold is:
%
\begin{equation}
	(\hat{\mu}_{ij} - k \hat{\sigma}_{ij}, \hat{\mu}_{ij} + k \hat{\sigma}_{ij}) \cap (-c, +c) = \emptyset
	\label{eqn:hyp-test-empty}
\end{equation}
%
This is equivalent to saying that $\hat{\mu}_{ij}$ is at least $k$ standard deviations away from the range $(-c, c)$. We choose to reject the null hypothesis $H_0$ if and only if equation \ref{eqn:hyp-test-empty} holds. This allows us to state with confidence greater than $\Phi(k)$ that either $W_{ij} < -c$ or $W_{ij} > c$ thus rejecting the null $H_0: |W_{ij}| \leq c$.

Note that we choose to accept $H_0$ even in the case that the combined probabilities of $p(W_{ij} < -c) + p(W_{ij} > c) > \Phi(k)$, if equation \ref{eqn:hyp-test-empty} is not satisfied. This is because we wish to apply this for dimensionality reduction purposes. We only want to keep weights for which we have a confident prediction outside the range $(-c, c)$ not those that succeed by summing the two extremes of their distribution. This case is very rare empirically but it nonetheless must be specified.

### 2021-06-01 cued/derivations.tex
Proof-read
Proof-read night before

We determine the form of $p(b| X)$ by integrating
out the parameters $\theta$. From the definitions, we have:
%
\begin{align*}
	p(b | X) &= \int p(b , \theta| X, \theta) d\theta = \int p(b | X, \theta) p(\theta | X) d\theta \\
	&=\int p(b | X, \theta) p(\theta) d\theta = \int \prod_{i \in [N] } \phi_{b_i}(x_i; \theta) p(\theta) d\theta \\
	&= \prod_{i \in [N]} \int \frac{\exp(w_{b_i}^T x_i) \prod_{j \in [B]} \Gaussian(w_j; 0, \sigma_\theta^2 I)}{\sum_{k \in [B]} \exp(w_{k}^T x_i)} dw_{1:B}.
\end{align*}
%
The key observation here is that 
the value of the integral is independent
of the value of $b_i \in [B]$ as
the integrand has the same form regardless of $b_i$. This is
because the prior is the same for each $w_j$. 
Therefore, the integral is only a function of $x_i$ and $\sigma_\theta^2$,
which means that, as a function of $b$, $p(b|X)\propto 1$. As
$b$ takes values in $[B]^N$, we necessarily have:
%
\begin{equation}
	p(b | X) = \frac{1}{\big|[B]^N\big|}=B^{-N}.
\end{equation}

@@

\subsection{Derivation of {\boldmath $\;\nabla U(\theta)$}}
\label{appdx:gradu}
Here we show how the gradient 
$\nabla U(\theta)$ can be computed explicitly.
Recall the expression for $U(\theta)$ in~(\ref{eqn:U-form}).
Writing $\theta$ as
$\theta = \left[w_1^T, w_2^T \dots w_B^T  \right]^T$,
in order to compute the gradient
$\nabla U(\theta)$ we need to compute
each of its components,
$\nicefrac{\partial U}{\partial w_k}$,
$1\leq k\leq B$.
To that end, we first compute,
%
\begin{align}
	\frac{\partial a_{ij}}{\partial w_k} &= \frac
	{\tilde{x}_i \exp(w_j^T \tilde{x}_i) \delta_{jk} \cdot \sum_{r \in [B]} \exp(w_r^T \tilde{x}_i) 
		- 
		\exp(w_j^T \tilde{x}_i) \cdot \tilde{x}_i \exp(w_k^T \tilde{x}_i)}
	{\left( \sum_{r \in [B]} \exp(w_r^T \tilde{x}_i) \right)^2} \nonumber \\
	&= \tilde{x}_i \left( a_{ij} \delta_{jk} - a_{ij}a_{ik} \right), 
	\label{eq:dadw}
\end{align}
%
where $\delta_{jk} \coloneqq \one \left\{ j = k \right\}$,
and we also easily find,
%
\begin{equation}
	\frac{ \partial}{\partial w_k} \|\theta\|^2 = \frac{\partial}{\partial w_k} \left( \sum_{r \in [B]} \|w_r\|^2 \right) = 2w_k.
	\label{eq:dtsdw}
\end{equation}
%
Using~(\ref{eq:dadw}) and~(\ref{eq:dtsdw}), we obtain,
\begin{align}
	\frac{\partial U}{\partial w_k} &= 
	\sum_{i \in [N]} \sum_{j \in [B]} y_{ij} 
	\left( -\frac{\tilde{x}_i}{a_{ij}} \left( a_{ij} \delta_{jk} - a_{ij} a_{ik} \right) \right)
	+ \frac{w_k}{\sigma_\theta^2} \nonumber \\
	&=  - \left( \sum_{i \in [N]} \tilde{x}_i \left( y_{ik} - a_{ik} \sum_{j \in [B]} y_{ij} \right)
	- \frac{w_k}{\sigma_\theta^2} \right) \nonumber \\
	&= - \left( \sum_{i \in [N]} \Big\{ \tilde{x}_i (y_{ik} - a_{ik}) \Big\} - \frac{w_k}{\sigma_\theta^2} \right).
\end{align}
%
This can be computed 
efficiently through matrix operations. The only property of $y_{ij}$ 
we have used in the derivation is the constraint $\sum_{j \in [B]} y_{ij} = 1$,
for all $i$.

>>>>

We determine the form of $p(b| X)$ by integrating
out the parameters $\theta$. From the definitions, we have:
%
\begin{align*}
	p(b | X) &= \int p(b , \theta| X, \theta) d\theta = \int p(b | X, \theta) p(\theta | X) d\theta \\
	&=\int p(b | X, \theta) p(\theta) d\theta = \int \prod_{i \in [N] } \phi_{b_i}(x_i; \theta) p(\theta) d\theta \\
	&= \prod_{i \in [N]} \int \frac{\exp(w_{b_i}^T x_i) \prod_{j \in [B]} \Gaussian(w_j; 0, \sigma_\theta^2 I)}{\sum_{k \in [B]} \exp(w_{k}^T x_i)} dw_{1:B}.
\end{align*}
%
The key observation here is that 
the value of the integral is independent
of the value of $b_i \in [B]$ as
the integrand has the same form regardless of $b_i$. This is
because the prior is the same for each $w_j$. 
Therefore, the integral can only be a function of at most $x_i$ and $\sigma_\theta^2$,
which means that, as a function of $b$, $p(b|X)\propto 1$. As
$b$ takes values in $[B]^N$, we necessarily have:
%
\begin{equation}
	p(b | X) = \frac{1}{\big|[B]^N\big|}=B^{-N}.
\end{equation}

@@

\subsection{Derivation of {\boldmath $\;\nabla U(\theta)$}}
\label{appdx:gradu}
Here we show how the gradient 
$\nabla U(\theta)$ can be computed explicitly.
Recall the expression for $U(\theta)$ in~(\ref{eqn:U-form}).
Writing $\theta$ as
$\theta = \left[w_1^T, w_2^T \dots w_B^T  \right]^T$,
in order to compute the gradient
$\nabla U(\theta)$ we need to compute
each of its components,
$\nicefrac{\partial U}{\partial w_k}$,
$1\leq k\leq B$.
To that end, we first compute,
%
\begin{align}
	\frac{\partial a_{ij}}{\partial w_k} &= \frac
	{x_i \exp(w_j^T x_i) \delta_{jk} \cdot \sum_{r \in [B]} \exp(w_r^T x_i) 
		- 
		\exp(w_j^T x_i) \cdot x_i \exp(w_k^T x_i)}
	{\left( \sum_{r \in [B]} \exp(w_r^T x_i) \right)^2} \nonumber \\
	&= x_i \left( a_{ij} \delta_{jk} - a_{ij}a_{ik} \right), 
	\label{eq:dadw}
\end{align}
%
where $\delta_{jk} \coloneqq \one \left\{ j = k \right\}$,
and we also easily find,
%
\begin{equation}
	\frac{ \partial}{\partial w_k} \|\theta\|^2 = \frac{\partial}{\partial w_k} \left( \sum_{r \in [B]} \|w_r\|^2 \right) = 2w_k.
	\label{eq:dtsdw}
\end{equation}
%
Using~(\ref{eq:dadw}) and~(\ref{eq:dtsdw}), we obtain,
\begin{align}
	\frac{\partial U}{\partial w_k} &= 
	\sum_{i \in [N]} \sum_{j \in [B]} y_{ij} 
	\left( -\frac{x_i}{a_{ij}} \left( a_{ij} \delta_{jk} - a_{ij} a_{ik} \right) \right)
	+ \frac{w_k}{\sigma_\theta^2} \nonumber \\
	&=  - \left( \sum_{i \in [N]} x_i \left( y_{ik} - a_{ik} \sum_{j \in [B]} y_{ij} \right)
	- \frac{w_k}{\sigma_\theta^2} \right) \nonumber \\
	&= - \left( \sum_{i \in [N]} \Big\{ x_i (y_{ik} - a_{ik}) \Big\} - \frac{w_k}{\sigma_\theta^2} \right).
\end{align}
%
This can be computed 
efficiently through matrix operations. The only property of $y_{ij}$ 
we have used in the derivation is the constraint $\sum_{j \in [B]} y_{ij} = 1$,
for all $i$.
